Estimating survival in left filtered data

### 2022-01-19 reports/04-gm.Rmd
soluble BS; get ready for sensitivity analysis with different distribution of R

gm_differences.tab <- gm_survival.tab[,.(
		Straight  = Straight[2] - Straight[1],
		Soluble   = Soluble[2] - Soluble[1],
		Synthetic = Synthetic[2] - Synthetic[1],
		Any = Any[2] - Any[1]
	), .(Estimator)]

@@

gm_cir.tab <- gm_ci.tab[,.(
		Straight  = Straight[2]/Straight[1],
		Soluble   = Soluble[2]/Soluble[1],
		Synthetic = Synthetic[2]/Synthetic[1],
		Any = Any[2]/Any[1]
	), .(Estimator)]

pander(gm_cir.tab)
```

>>>>

gm_differences.tab <- gm_survival.tab[,.(
		Straight  = Straight[2] - Straight[1],
		Soluble   = Soluble[2] - Soluble[1],
		Synthetic = Synthetic[2] - Synthetic[1]
		# Any = Any[2] - Any[1]
	), .(Estimator)]

@@

gm_cir.tab <- gm_ci.tab[,.(
		Straight  = Straight[2]/Straight[1],
		Soluble   = Soluble[2]/Soluble[1],
		Synthetic = Synthetic[2]/Synthetic[1]
		# Any = Any[2]/Any[1]
	), .(Estimator)]

# pander(gm_differences.tab); pander(gm_cir.tab)
```
